Data Management \\ and LSST Special Programs

### 2022-02-21 DMTN-065.tex
update hardbounds pointing
fix WFD definition

\subsection{Wide-Fast-Deep (WFD) Main Survey}\label{ssec:terms_wfd}
The WFD Main Survey is the core science program of the LSST, designed to achieve the science goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).
The WFD will cover at least $\sim$18000 deg$^2$ and is expected to be accomplished with 85--90\% of the observing time.
As of the Phase 1 SCOC recommendations in \citeds{PSTN-053}, the WFD Main Survey is thought of as several contiguous areas.
The largest is the low-dust-extinction survey area, which would also receive the most ($>$800) visits over the 10-year survey and be completed to uniform depth, likely with a rolling cadence.
Smaller regions cover the higher-extinction high stellar density Galactic Bulge and Magellanic Clouds, the North Ecliptic Spur (NES), and the remainder of the Galactic Plane and the South Celestial Pole.
Boundaries, re-visit cadences, and depths for all WFD areas remain to be determined \citedsp{PSTN-053}.

\subsubsection{Mini-Surveys}\label{sssec:terms_wfd_mini}
As of the Phase 1 SCOC recommendations in \citeds{PSTN-053}, the term ``mini-survey" was being used to refer to the areas of the WFD / Main Survey outside of the large, low-dust-extinction survey area.
This term used to refer to non-WFD regions (Special Programs).

\subsection{Special Programs}\label{ssec:terms_sp}
Special Programs are additional survey areas and/or observing strategies that are driven by specific science goals which either build on, or are outside of, the core science pillars of the LSST.
Special Programs will fill the remaining 10--15\% of the available survey time, and include both ``deep drilling" fields and ``micro-surveys".

@@

>>>>

\subsection{Wide-Fast-Deep (WFD) Main Survey}\label{ssec:terms_wfd}
The WFD Main Survey is the core science program of the LSST, designed to achieve the science goals defined by the Science Requirements Document (SRD; \citeds{LPM-17}).
As of the Phase 1 SCOC recommendations in \citeds{PSTN-053}, the WFD Main Survey is thought of as several contiguous areas that cover at least $\sim$18000 deg$^2$ with $\gtrsim$800 visits per field, and is expected to be accomplished with $\sim$85\% of the observing time.
These areas include the low-dust-extinction survey area (the largest area), the higher-extinction high stellar density Galactic Bulge, and the Magellanic Clouds.

\subsection{Mini-Surveys}\label{sssec:terms_wfd_mini}
As of the Phase 1 SCOC recommendations in \citeds{PSTN-053}, the term ``mini-survey" refers to additional areas that are adjacent to the WFD but are covered with a few hundred (100-300) visits per pointing.
They are expected to be accomplished with $\sim$10\% of the total survey time.
Mini-surveys include the North Ecliptic Spur (NES), the remainder of the Galactic Plane, and the South Celestial Pole.
Boundaries, re-visit cadences, and depths for all WFD areas remain to be determined \citedsp{PSTN-053}.

\subsection{Special Programs}\label{ssec:terms_sp}
Special Programs are survey areas and/or observing strategies, aside from the WFD and mini-surveys, that are driven by specific science goals which either build on, or are outside of, the core science pillars of the LSST.
Special Programs will fill the remaining $\sim$5\% of the available survey time, and include both ``deep drilling" fields and ``micro-surveys".

@@

Special Programs which required the \emph{exact same} field pointing and rotation for \emph{every exposure} (to sub-arcsecond levels) might run into hardware boundaries on pointing and tracking, but none of the currently-proposed programs seem likely to be affected by this potential boundary.
